### 2022-01-05 experiments.tex
writing

\todo[inline]{WIP}

In this section, we aim to validate the utility of the CLEAVE framework through a series of experiments.
In particular, we wish to show the utility of CLEAVE as a tool for repeatable and scalable benchmarking of \acp{NCS} in Edge environments.

\todo[inline]{talk about goal of experiments}

@@

We depict our experimental setup in \cref{fig:cleave:expsetup}, consisting of a single control loop deployed across a pair of consumer-grade computing devices.
We employ a Raspberry Pi 4B single-board computer together with a general-purpose \verb|x86_64|-based workstation; the \ac{OS} configured on both corresponds to Ubuntu Server 20.04 LTS~\cite{Ubuntu}.
These devices are connected to each other by an 802.11n WiFi link.
For ease of orchestration and re-parametrization, as well as to mimic real-world deployments, we package our CLEAVE control loop as a pair of Docker~\cite{merkel2014docker} containers.
For our main set of experiments, a two-node Docker \emph{Swarm}~\cite{Swarm2021} is set up with the \verb|x86_64| host configured as a Manager and the Raspberry Pi as a Worker node.
The containers are deployed inside the Swarm, with one of them configured as a Controller, assigned to the \verb|x86_64| host, and the other one as the Inverted Pendulum Plant and assigned to the Raspberry Pi.
These instances communicate over an overlay network which sits on top of and abstracts away the real network configuration.
Additionally, to obtain baseline results without the stochastic effects of the network, we employ a secondary ``local-only'' setup, in which we simply execute both Plant and Controller containers co-located on the \verb|x86_64| host.

@@

>>>>

\input{tables/hardware.tex}

In this section, we demonstrate the practical utility of \ac{CLEAVE} through a series of experiments on an emulated \ac{NCS} running between a client device and a cloudlet.
We aim to answer question relating to the ability of our framework to provide relevant, accurate, and repeatable measurements of the performance of \acp{NCS} deployed on edge computing infrastructure.

@@

We depict our experimental edge setup in \cref{fig:cleave:expsetup}, consisting of a single control loop deployed across a pair of consumer-grade computing devices.
We employ a Raspberry Pi 4B single-board computer as a client device, together with a general-purpose \verb|x86_64|-based workstation which acts as the cloudlet.
These devices are connected to each other by an 802.11n WiFi link.
For ease of orchestration and re-parametrization, as well as to mimic real-world deployments, we package our CLEAVE control loop as a pair of Docker~\cite{merkel2014docker} containers.
For our main set of experiments, a two-node Docker \emph{Swarm}~\cite{Swarm2021} is set up with the cloudlet host configured as a Manager and the client device as a Worker node.
The containers are deployed inside the Swarm, with one of them configured as a Controller, assigned to the cloudlet, and the other one as the Inverted Pendulum Plant and assigned to the client.
These instances communicate using the \ac{UDP} over an overlay network which sits on top of and abstracts away the real network configuration.
Additionally, to obtain baseline results without the stochastic effects of the network, we employ a secondary ``local-only'' setup, in which we simply execute both Plant and Controller containers co-located on the cloudlet.

@@

The results presented below provide valuable insights on both system limits and on the chosen \ac{NCS} itself, as well as on the capabilities of \ac{CLEAVE}.

We begin with a simple analysis of the stability of the Plant.
\Cref{fig:topple:fraction} shows a visualization of the fraction of plants that toppled in each scenario.
It provides a very clear overview of the minimum requirements

\begin{figure}
    \centering
    \includegraphics[width=.8\columnwidth]{topple_fraction.png}
    \caption{Fraction of plants that toppled, per experimental setup.}%
    \label{fig:topple:fraction}
\end{figure}

When it comes to network reliability, mean packet losses for all setups were below \SI{0.15}{\percent}. 
\todo[inline]{Discuss which network results to add.}
